Update Meeting: 03-11-2021

### 2021-11-02 analysis/update_meeting_03_11_2021.Rmd
wflow_publish("analysis/update_meeting_03_11_2021.Rmd")

The columns `IVW_meta_beta` and `IVW_meta_pval` correspond to the meta-analyzed across sexes univariate results from the $Y_p ~ X_i$ MR. The subsequent columns correspond to the MVMR MR results.

```{r MVMR_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE)}

@@

household_MR_summary_sub <- household_MR_summary %>% dplyr::select(exposure_ID, outcome_ID, IVW_meta_beta, IVW_meta_pval) %>% unique()
MVMR_uniMR_comparison.DT <- inner_join(household_MR_summary_sub, household_MVMR_BF.DT)
format_round_cols <- colnames(dplyr::select_if(MVMR_uniMR_comparison.DT, is.numeric))

DT::datatable(MVMR_uniMR_comparison.DT, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3) %>% dplyr::select(exposure_ID, outcome_ID, exposure_description, outcome_description, corr_traits, everything())

>>>>

The column `corr_traits` corresponds to the raw correlation between traits in the biobank. The columns `IVW_meta_beta` and `IVW_meta_pval` correspond to the meta-analyzed across sexes univariate results from the $Y_p ~ X_i$ MR. The subsequent columns correspond to the MVMR MR results.

```{r MVMR_summary, echo = FALSE, eval = ifelse(Sys.info()["sysname"]=="Linux", TRUE, FALSE), message=FALSE}

@@

household_MR_summary_sub <- household_MR_summary %>% dplyr::select(exposure_ID, outcome_ID, IVW_meta_beta, IVW_meta_pval) %>% unique()
MVMR_uniMR_comparison.DT <- inner_join(household_MR_summary_sub, household_MVMR_BF.DT)  %>% dplyr::select(exposure_ID, outcome_ID, exposure_description, outcome_description, corr_traits, everything())
format_round_cols <- colnames(dplyr::select_if(MVMR_uniMR_comparison.DT, is.numeric))

DT::datatable(MVMR_uniMR_comparison.DT, width = "100%") %>% formatRound(columns=format_round_cols, digits = 3)
